### 2014-07-03 tex/proofs.tex
Added amsthm package to preamble

\subsubsection{State Representation Relation}
A symbolic system state represents a set of lazy system states. To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ . The representation relationship is defined as follows: $\mathcal{L}\sqsubseteq \mathcal{S} $ if and only if there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$

@@

>>>>

\begin{definition}{State Representation}
A symbolic system state represents a set of lazy system states. To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ . The representation relationship is defined as follows: $\mathcal{L}\sqsubseteq \mathcal{S} $ if and only if there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$
\end{definition}

\begin{definition}{Exact Symbolic State}
A symbolic state $\mathcal{S}$ is \textbf{exact} if and only if it represents the set of all feasible lazy states on the current execution path, and represents no infeasible state.
\end{definition}

@@

\begin{lemma}
If symbolic state $\mathcal{S}$ is exact prior to executing the Field Access rule, then the state $\mathcal{S}^\prime$ is also exact.
\end{lemma}

\begin{proof}
Suppose that all relevant fields are initialized. Take an arbitrary lazy state $\mathcal{L} \sqsubset \mathcal{S}$ and execute the lazy field access rule to achieve state $\mathcal{L}^\prime$. Note that by rule, $\mathcal{L} = The only differences between  $\mathcal{L}$ and  $\mathcal{L}^\prime$ are the
\end{proof}
